\sysfull

### 2018-08-06 paper/asplos19/hwswsetup.tex
Minor changes to section 7

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{| r|r|r | p{0.54\columnwidth} |}
		\hline
		App.&tasks&SLOC&Description\\
		\hline\hline
        \textbf{ar} &10 &428 & Activity recognition using a nearest neighbor
classifier\\ % with a deterministic input from a randomly-generated sequence of accelerometer data\\
		\hline
        \textbf{bc} &10 &371 & Counts bits in bytes sequences
using several algorithms and check for correctness\\
		\hline
        \textbf{cuckoo} &14 &426 & Inserts and queries a sequence of pseudo-random
values in a Cuckoo filter.\\
		\hline
        \textbf{dijkstra} &5 &198 & Dijkstra shortest path algorithm \\
		\hline
        \textbf{fft} &8 &449 & Fast Fourier Transform\\ % on three pre-generated 128 sample vectors\\
		\hline
		\textbf{sort} &4 &167 & Selection sort algorithm\\
		\hline
	\end{tabular}
\caption{Description and characteristics of benchmark applications used to
evaluate \sys.}
\label{table:benchmark_table}
\end{table}

We evaluated \sys using six benchmarks that are oftenly used in embedded systems (summarized in
Table~\ref{table:benchmark_table}). All applications were compiled using MSP430 GCC~\cite{ti-gcc} version 6.4.0 toolchain with \texttt{-O1} as optimization flag. The source code for all benchmarks will be released at \cite{coala_website}.\\
%
\textbf{Comparison with Alpaca using the GCC compiler.} We compare
\sys against Alpaca~\cite{alpaca}, the state-of-the-art task-based system for
intermittent computing. For a fair comparison the task decomposition of the benchmarks are ensured to be the
same for both systems.\\
%
Since Alpaca's compiler pass is implemented only for LLVM, we could not use
that implementation to instrument the benchmarks and compile them with GCC.
Instead, we \emph{manually} performed the instrumentation done by the compiler
pass. The instrumentation consists of identifying write-after-read dependencies 
and adding code and memory allocations to make a private copy of the affected variables. 
For array variables, instrumentation also includes adding code for 
dynamically tracking the array access. Manual instrumentation of Alpaca code is not a general approach, 
but only served as a practical alternative to porting the compiler pass from LLVM to GCC.
%
Our experiments show that manually-instrumented Alpaca code compiled with GCC
is about 30\%-40\% faster than Alpaca code instrumented automatically by the
Alpaca LLVM compiler pass and compiled with LLVM. This performance difference
is due to the early experimental state of the MSP430 backend for
LLVM~\cite{baghsorkhi_cgo_2018}.
%
By compiling both systems with the same compiler (GCC), we ensure that our
comparison in Section~\ref{sec:evaluation} is fair.

>>>>

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{| r|r|r | p{0.54\columnwidth} |}
		\hline
		App.&tasks&SLOC&Description\\
		\hline\hline
        \textbf{ar} &10 &428 & activity recognition using a KNN\\ % with a deterministic input from a randomly-generated sequence of accelerometer data\\
		\hline
        \textbf{bc} &10 &371 & several bitcount algorithms\\
        % \textbf{bc} &10 &371 & Counts bits in bytes sequences
% using several algorithms and check for correctness\\
		\hline
        \textbf{cuckoo} &14 &426 & inserts and queries a sequence of pseudo-random
values in a Cuckoo filter\\
		\hline
        \textbf{dijkstra} &5 &198 & Dijkstra shortest path algorithm \\
		\hline
        \textbf{fft} &8 &449 & Fast Fourier Transform\\ % on three pre-generated 128 sample vectors\\
		\hline
		\textbf{sort} &4 &167 & selection sort algorithm\\
		\hline
	\end{tabular}
\caption{Characteristics of benchmarks used for evaluation.}
\label{table:benchmark_table}
\end{table}

We evaluated \sys using six benchmarks that are oftenly used in embedded systems (summarized in
Table~\ref{table:benchmark_table}). All applications were compiled using MSP430 GCC~\cite{ti-gcc} version 6.4.0 toolchain with \texttt{-O1} as optimization flag. The source code for all benchmarks will be released at \cite{coala_website}.

\paragraph{Comparison with Alpaca using the GCC compiler.}

We compare \sys against Alpaca~\cite{alpaca}, the state-of-the-art task-based system for
intermittent computing. For a fair comparison the task decomposition of the benchmarks are ensured to be the
same for both systems.
%
\note{try to reduce what follows}
%
Since Alpaca's compiler pass is implemented only for LLVM, we could not use
that implementation to instrument the benchmarks and compile them with GCC.
Instead, we \emph{manually} performed the instrumentation done by the compiler
pass. The instrumentation consists of identifying write-after-read dependencies 
and adding code and memory allocations to make a private copy of the affected variables. 
For array variables, instrumentation also includes adding code for 
dynamically tracking the array access. Manual instrumentation of Alpaca code is not a general approach, 
but only served as a practical alternative to porting the compiler pass from LLVM to GCC.
%
Our experiments show that manually-instrumented Alpaca code compiled with GCC
is about 30\%-40\% faster than Alpaca code instrumented automatically by the
Alpaca LLVM compiler pass and compiled with LLVM. This performance difference
is due to the early experimental state of the MSP430 backend for
LLVM~\cite{baghsorkhi_cgo_2018}.
%
By compiling both systems with the same compiler (GCC), we ensure that our
comparison in Section~\ref{sec:evaluation} is fair.
